LAGOS lake depth

### 2020-02-26 figures/01_heatmap.Rmd
add true metrics correlation figure

>>>>

```{r metric_correlations_setup, echo=FALSE, warning=FALSE}

dt <- dplyr::select(dt_raw_ne, names(dt_raw_ne)[names(dt_raw_ne) %in%
                    c("lake_meandepth_m", 
              names(readRDS("../data/01_depth_model/depth_training.rds")))])
names(dt) <- gsub("^lake_", "", names(dt))

gg_slope <- jsta::jheatmap(dt, focal_columns = "inlake_slope")$gtable
gg_dist <- jsta::jheatmap(dt, focal_columns = "dist_deepest")$gtable
```

```{r metric_correlations, echo=FALSE, warning=FALSE}
cowplot::plot_grid(
  gg_slope, 
  gg_dist, 
  rel_widths = c(1, 0.95))
```
